Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-12-06 document/submission/ms.tex
Global replace all the ambient with hot photosphere, and starspot with cool photosphere.

Ages and masses of young stars are often estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but nonstandard physics like magnetic fields and starspots complicate this process. In order to understand their influence, we study in detail the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.  We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.  Spectral features are attributable to both an ambient photosphere $\teffa\sim4100$ K and to cool starspots $\teffb\sim2700-3000$ K, which imply a best fit filling factor of $f\sim80$\% starspots at the time of the observation. These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively support the picture of an extremely heavily spotted star with secularly changing starspot filling factors and temperature contrasts through time. A persistent hotspot covering $\sim20$\% of the surface is a plausible alternative explanation. The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous measurements, a bias likely afflicting most young, heavily spotted stars, and which likely contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters. We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.

@@

Starspots possess a spectrum distinct from the ambient photosphere.  Approaches like ZDI and line-bisector analysis \citep[\emph{e.g.}][]{prato08, donati14} target the modulation of stellar photospheric lines as starspots enter and exit the observable stellar disk.  In contrast, the technique described in this Section detects and measures the emergent spectrum originating from cool starspots.

@@

The choice of nomenclature depends on the physical origin of the emission region.  In general, the emission region's physical origin is not directly observable without ancillary information.  For many applications, it could be reasonably assumed that the cool photospheric component corresponds to a sunspot or sunspot group, and the hot component corresponds to the ambient photosphere.  However, a cool ambient photosphere possessing localized hot spots---like plages on the sun---could yield the same or similar two-temperature composite spectrum.  In principle the physical origin could be assessed with detailed comparision of average surface magnetic field strengths through Zeeman line broadening or other magnetic-field sensitive techniques.  We made no effort to make such an assessment in this work, and therefore index the two photospheric components in the most general way possible, simply \emph{cool} and \emph{hot}.

@@

\begin{figure*}
 \centering
 \includegraphics[width=0.95\textwidth]{violin_Teff_fill_order} 
 \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\mathrm{cool}}$ (yellow shade).  The stellar parameters are derived independently in each spectral order.  Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=104, 102, 100, 88, 83$) showing tight constraints on the filling factor of starspots.  The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.  $K-$band orders show lower estimates for the ambient photosphere, though many of these estimates are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
 \label{fig:TwoTempResults}
\end{figure*}

@@

The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.  Starspots are cooler than their surrounding photosphere and will therefore have a longer wavelength of peak emission.  The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptoting to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.  The bottom panel of Figure \ref{fig:SingleTeffvsOrder} shows the flux density ratio for patches of photosphere with equal areas (50\% filling factor) but different temperatures-- 2800 K and 4100 K for the starspot and ambient photosphere respectively.  The black-body ratios predict smooth flux ratio increases with wavelength, while the ratio of \PHOENIX\ models shows wavelength regions with heightened sensitivity to starspot fluxes, for example in $J-$band.

@@

The IGRINS spectrum demonstrates some features that are present only in the ambient photosphere model, and some features that are present only in the starspot model.  Figure \ref{fig:specPostageStamp} shows a selection of six such spectral features for a range of plausible fill factors.  In some cases (\emph{e.g.} the top two panels), featureless starspot spectra veil isolated spectral lines predicted in the ambient photosphere models.  In other cases (\emph{e.g.} the middle row and lower left panel), the ambient photosphere model veils sequences of shallow spectral features predicted in the starspot model.  The starspot spectral models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotational broadening.  Any feature of interest will be biased to non-zero veiling.

The combination of line blanketing and high $\vsini$ has probably hampered efforts to identify isolated spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.  One such feature, the OH 1.563 $\mu$m line noted by \citet{oneal01}, shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines.  The \PHOENIX\ models predict a non-negligible ambient photosphere contribution to the middle line for our range of ambient and spot temperatures.  In comparison, the forward-modeling technique described in this work thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.  The level of veiling of ambient photospheric lines is set by the starspot filling factor and temperature, while the level of veiling of the starspot lines is set by the filling factor and temperature of the ambient photosphere lines. Similar forward-modelling strategies have successfully identified patterns of weak metal lines in the line-blanketed spectra of low metallicity stars \citep{kirby11,kirby15}.  Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} in the Appendix show 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.

@@

Best fit values for the stellar parameters summarized are listed in Table \ref{tbl_adopted_props}.  Remarkably, the filling factor of starspots exceeds 50\%, with a best fit value of $f_{\mathrm{cool}}=80\pm 5 \% $.

@@

In the previous section, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a two-temperature photosphere.  In this section, we test fit by comparing the combined spectrum to observed spectral features and rotational modulation.  We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4100 K covering 20\% of the stellar surface, obtained when LkCa 4 had an estimated brightness of $V=12.84$ mag.  The starspot and ambient temperatures and the filling factor are blindly adopted without any adjustments to attempt to improve fits to the SED or broadband spectra.

Figures~\ref{fig:sed}-\ref{fig:lores} compares synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.  The only free parameters in this comparison are the luminosity and extinction, which are both scaled to match the spectrum (see \S 5.1-5.2).  The optical-IR SED is obtained by estimating photometry from \citet{grankin08} during the 2MASS epoch, with $V\sim12.61$ mag (see Table~1).  The SED also includes mid-IR photometry from Spitzer/IRAC \citep{hartmann05}, without adjusting for epoch.  In the spectroscopic comparison, some minor discrepancies between the optical and near-IR spectra may be introduced because the spot coverage changed in the $\sim 5$ hrs between observations ($\Delta V=0.08$ mag).  The synthetic spectrum is obtained from the Phoenix models, as in \S 3, and is extended beyond the longest wavelength (5 $\mu$m) to calculate the bolometric luminosity.

@@

%Furlan:  K7, V-IC=1.92, E(V-I)=1.6 => 0.85 mag;  close enough to their 1.1 mag
%V-K = 4.18  ; MS colors:  3.16 (KH95) => Av=1.1 mag

%V-J:  2.8-3.8
%J-K:  0.9-1.0

%\begin{table}
%\caption{Predicted Photometric Range}
%\centering
%\label{tab:photrange}
%\begin{tabular}{cccc}
%\hline
%Band & Low Spot & High Spot & Range\\
%Cool Spot & 68\% & 83\% &\\
%\hline
%\multicolumn{4}{c}{Based on $V$, need to adapt for $A_V$}\\
%$B$ & 13.80 & 14.48 & 0.68\\
%$V$ & 12.56 & 13.23 & 0.67\\
%$R$ & 11.53 & 12.17 & 0.64 \\
%$I$ & 10.80 & 11.38 & 0.58\\
%$J$ & 9.79 & 10.00 & 0.21\\
%$K$ & 8.89 & 9.04 & 0.15\\
%\hline
%\end{tabular}
%\end{table}

@@

In this paper, we have demonstrated that IGRINS spectra of LkCa 4 is well modeled with two temperatures, an ambient photosphere of 4100 K and large cool spots of 2700--3000 K that cover 80\% of the stellar surface.  This solution reproduces the high-resolution HK spectra obtained with IGRINS, the broadband SED, and rotational modulation of spectral features.  Such a high covering fraction for a spot is extraordinary.  In this section, we describe that this type of cool spot is robust, despite some simplifying limitations of our spectral inference technique, discuss how such a large spot could be interpreted, and suggest that, while LkCa 4 appears extreme, other young sources have similar characteristics.

@@

Large amplitudes of the light variation indicate the existence of very extended spotted regions on the stellar surface. To estimate the total area and mean temperature of the spots in the visible stellar hemisphere Grankin used a simple non-parametric model for analysis of V410 Tau, V819 Tau, V827 Tau, and V830 Tau \citep{grankin98,grankin99}.  For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the spots is $500-1400$ K lower than the ambient photosphere.  An analysis of the calculated spot parameters of V410 Tau revealed that there is a real correlation between the amplitude of periodicity and the spot distribution
nonuniformity, which is defined as the difference of spot coverage in the visible hemispheres of the star at maximum and minimum light. As the amplitude increases from 0.39 to 0.63 mag, the degree of nonuniformity in the spot distribution increases from 21 to 37\%.  An alternative analysis of TiO bands indicate a spot coverage of $\sim 41$\% for V410 Tau \citep{petrov94}.  Besides the high amplitude of variability, these objects show the phenomenon of long-term stability of a brightness minimum in the interval from 5 to 19 years.  To all appearances, this group of stars has the similar nature of stellar activity which should be investigated in the future.  
%The stars all have similar optical spectral types \citep[e.g.][]{kenyon95,herczeg14}.

%The number of WTTS for which the areal filling factor of spots have been measured is relatively low.  
%Recently there have been many new estimates.

% Grankin

% Covey
The Pleiades serves as an older age sample of young stars possessing evidence for large coverage fraction of starspots.  For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}, while LAMOST spectra of the TiO band indicates that $\sim 30$\% spot coverages may be common for 3500--5000 K stars \citep{fang2016}.  Recent photometric monitoring of the Pleiades indicates that the anomalous colors scale with rotation rate, strengthing the case for magnetic-field induced starspots as the cause of the anomaly \citep{covey16}.  However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude at the precision of the PTF data, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.  LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation.  The longitudinally symmetric component evades photometric modulation detection, but contributes to otherwise anomalous color offsets.

% Venuti

@@

We assume only two temperature components present in the photosphere.  In reality, starspots are probably described by a range of spot temperatures analogous to umbra, penumbra, and plages on the solar surface.  A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better and could lead to the possibility of overfitting.  The fit-quality of the existing two-temperature fits seems fairly strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents must be relatively low.  Interestingly, $K-$band has several spectral orders that converge towards hybrid temperatures in the vicinity of $\sim3500$ K.  Most of these orders are flagged as erroneous due to strong metal line spectral outliers or uncorrected calibration artifacts.  A few orders just show mediocre fits where no permutation of hot and cool two-temperature models could describe all of the variance in the spectrum.  These $K-$band orders could be examined for a penumbra-like temperature component.  We caution that systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.  Space-based high-precision planetary transit spectrophotometry could offer an avenue to measure the morphologies and temperature distributions of starspots for the subset of transiting exoplanet host stars or eclipsing binaries.

@@

\section{Conclusions}
This paper establishes that the optical+near-IR spectrum of the weak-lined T Tauri star LkCa 4 includes multiple components.  When fit with two temperatures, the ambient photosphere of 4100 K covers 20\% of the stellar surface while the cool spot of 2700--3000 K covers 80\% of the stellar surface.  The previously-established $V$-band brightness variability of $0.8$ mag is interpreted as the rotational modulation of the covering fraction of the hot spot.  This spectral modelling leads to an improved effective temperature measurement of LkCa 4.

>>>>

Ages and masses of young stars are often estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but nonstandard physics like magnetic fields and starspots complicate this process. In order to understand their influence, we study in detail the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.  We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.  Clearly discernable spectral features arise from both a hot photospheric component $\teffa\sim4100$ K and to a cool component $\teffb\sim2700-3000$ K, which imply a best fit filling factor of cool photosphere of $f_{\mathrm{cool}}\sim80$\% at the time of the observation. These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively support the picture of either an extremely heavily spotted star or a hotspot covering $\sim20$\% of the surface.  The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates and naively using the same model tracks.  Biases from starspots likely afflict most young, heavily spotted stars, and likely contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters. We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.

@@

Starspots possess a spectrum distinct from the ambient photosphere.  Approaches like ZDI and line-bisector analysis \citep[\emph{e.g.}][]{prato08, donati14} target the modulation of stellar photospheric lines as starspots enter and exit the observable stellar disk.  In contrast, the technique described in this Section detects and measures the emergent spectrum originating from patches of cool starspots.

@@

The choice of nomenclature depends on the physical origin of the emission region.  In general, the emission region's physical origin is not directly observable without ancillary information.  For many applications, it could be reasonably assumed that the cool photospheric component corresponds to a sunspot or sunspot group, and the hot component corresponds to the ambient photosphere.  However, a cool ambient photosphere possessing localized hot spots---like plages on the sun---could yield the same or similar two-temperature composite spectrum.  In principle, the physical origin could be assessed with detailed comparision of average surface magnetic field strengths through Zeeman line broadening or other magnetic-field sensitive techniques.  We made no effort to make such an assessment in this work, and therefore index the two photospheric components in the most general way possible, simply \emph{cool} and \emph{hot}.

@@

\begin{figure*}
 \centering
 \includegraphics[width=0.95\textwidth]{violin_Teff_fill_order} 
 \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\mathrm{cool}}$ (yellow shade).  The stellar parameters are derived independently in each spectral order.  Spectral orders show differing levels of constraint on the cool photosphere and hot photosphere properties, with some ($o=104, 102, 100, 88, 83$) showing tight constraints on the filling factor of starspots.  The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.  $K-$band orders show lower estimates for the hot photosphere, though many of these estimates are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
 \label{fig:TwoTempResults}
\end{figure*}

@@

The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.  Starspots are cooler than their surrounding photosphere and will therefore have a longer wavelength of peak emission.  The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptoting to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.  The bottom panel of Figure \ref{fig:SingleTeffvsOrder} shows the flux density ratio for patches of photosphere with equal areas (50\% filling factor) but different temperatures-- 2800 K and 4100 K for the cool and hot photosphere respectively.  The black-body ratios predict smooth flux ratio increases with wavelength, while the ratio of \PHOENIX\ models shows wavelength regions with heightened sensitivity to starspot fluxes, for example in $J-$band.

@@

The IGRINS spectrum demonstrates some features that are present only in the hot photosphere model, and some features that are present only in the cool photosphere model.  Figure \ref{fig:specPostageStamp} shows a selection of six such spectral features for a range of plausible fill factors.  In some cases (\emph{e.g.} the top two panels), featureless cool photosphere spectra veil isolated spectral lines predicted in the hot photosphere models.  In other cases (\emph{e.g.} the middle row and lower left panel), the hot photosphere model veils sequences of shallow spectral features predicted in the cool photosphere model.  The cool spectral models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotational broadening; any feature of interest will be biased to non-zero veiling.

The combination of line blanketing and high $\vsini$ has probably hampered efforts to identify isolated spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.  One such feature, the OH 1.563 $\mu$m line noted by \citet{oneal01}, shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines.  The \PHOENIX\ models predict a non-negligible hot photosphere contribution to the middle line for our range of hot and cool temperatures.  In comparison, the forward-modeling technique described in this work thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.  The level of veiling of hot photospheric lines is set by the cool photosphere filling factor and temperature, while the level of veiling of the cool lines is set by the filling factor and temperature of the hot photosphere lines. Similar forward-modelling strategies have successfully identified patterns of weak metal lines in the line-blanketed spectra of low metallicity stars \citep{kirby11,kirby15}.  Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} in the Appendix show 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.

@@

Best fit values for the stellar parameters are listed in Table \ref{tbl_adopted_props}.  Remarkably, the filling factor of cool photosphere exceeds 50\%, with a best fit value of $f_{\mathrm{cool}}=80\pm 5 \% $.

@@

In the previous section, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a two-temperature photosphere.  In this section, we test the two component fit by comparing the combined spectrum to observed spectral features and rotational modulation.  We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4100 K covering 20\% of the stellar surface, obtained when LkCa 4 had an estimated brightness of $V=12.84$ mag.  The cool and hot temperatures and the filling factor are blindly adopted without any adjustments to attempt to improve fits to the SED or broadband spectra.

Figures~\ref{fig:sed}-\ref{fig:lores} compare synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.  The only free parameters in this comparison are the luminosity and extinction, which are both scaled to match the spectrum (see \S 5.1-5.2).  The optical-IR SED is obtained by estimating photometry from \citet{grankin08} during the 2MASS epoch, with $V\sim12.61$ mag (see Table~1).  The SED also includes mid-IR photometry from Spitzer/IRAC \citep{hartmann05}, without adjusting for epoch.  In the spectroscopic comparison, some minor discrepancies between the optical and near-IR spectra may be introduced because the spot coverage changed in the $\sim 5$ hrs between observations ($\Delta V=0.08$ mag).  The synthetic spectrum is obtained from the Phoenix models, as in \S 3, and is extended beyond the longest wavelength (5 $\mu$m) to calculate the bolometric luminosity.

@@

@@

In this paper, we have demonstrated that IGRINS spectra of LkCa 4 is well modeled with two temperatures, a hot photosphere of 4100 K and large cool patches of 2700--3000 K that cover 80\% of the stellar surface.  This solution reproduces the high-resolution HK spectra obtained with IGRINS, the broadband SED, and rotational modulation of spectral features.  Such a high covering fraction for a spot is extraordinary.  In this section, we describe that this type of cool spot is robust, despite some simplifying limitations of our spectral inference technique, discuss how such a large spot could be interpreted, and suggest that, while LkCa 4 appears extreme, other young sources have similar characteristics.

@@

Large amplitudes of the light variation indicate the existence of very extended spotted regions on the stellar surface. To estimate the total area and mean temperature of the spots in the visible stellar hemisphere Grankin used a simple non-parametric model for analysis of V410 Tau, V819 Tau, V827 Tau, and V830 Tau \citep{grankin98,grankin99}.  For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the cool regions is $500-1400$ K lower than the ambient photosphere.  An analysis of the calculated spot parameters of V410 Tau revealed that there is a real correlation between the amplitude of periodicity and the spot distribution
nonuniformity, which is defined as the difference of spot coverage in the visible hemispheres of the star at maximum and minimum light. As the amplitude increases from 0.39 to 0.63 mag, the degree of nonuniformity in the spot distribution increases from 21 to 37\%.  An alternative analysis of TiO bands indicate a spot coverage of $\sim 41$\% for V410 Tau \citep{petrov94}.  Besides the high amplitude of variability, these objects show the phenomenon of long-term stability of a brightness minimum in the interval from 5 to 19 years.

The Pleiades serves as an older age sample of young stars possessing evidence for large coverage fraction of starspots.  For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}, while LAMOST spectra of the TiO band indicates that $\sim 30$\% spot coverages may be common for 3500--5000 K stars \citep{fang2016}.  Recent photometric monitoring of the Pleiades indicates that the anomalous colors scale with rotation rate, strengthing the case for magnetic-field induced starspots as the cause of the anomaly \citep{covey16}.  However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude at the precision of the PTF data, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.  LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation.  The longitudinally symmetric component evades photometric modulation detection, but contributes to otherwise anomalous color offsets.

@@

We assume only two temperature components present in the photosphere.  In reality, starspots are probably described by a range of spot temperatures analogous to umbra, penumbra, and plages on the solar surface.  A model possessing three unique temperatures and two unique fill factors would better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better and could lead to the possibility of overfitting.  The fit-quality of the existing two-temperature fits seems strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents must be relatively low.  Interestingly, $K-$band has several spectral orders that converge towards hybrid temperatures in the vicinity of $\sim3500$ K.  Most of these orders are flagged as erroneous due to strong metal line spectral outliers or uncorrected calibration artifacts.  A few orders just show mediocre fits where no permutation of hot and cool two-temperature models could describe all of the variance in the spectrum.  These $K-$band orders could be examined for a penumbra-like temperature component.  We caution that systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.  Space-based high-precision planetary transit spectrophotometry could offer an avenue to measure the morphologies and temperature distributions of starspots for the subset of transiting exoplanet host stars or eclipsing binaries.

@@

\section{Conclusions}
This paper establishes that the optical and near-IR spectra of the weak-lined T Tauri star LkCa 4 include multiple components.  When fit with two temperatures, the hot photosphere of 4100 K covers 20\% of the stellar surface while the cool photospheric component of 2700--3000 K covers 80\% of the stellar surface.  The previously-established $V$-band brightness variability of $0.8$ mag is interpreted as the rotational modulation of the covering fraction of the hot photospheric component.  This spectral modelling leads to an improved effective temperature measurement of LkCa 4.
